```{r}
#| echo: false

psy_511_vars <- readr::read_csv("data/csv/psy-511-vars.csv", show_col_types = FALSE)
```

---

## Week 01: Jan 12-16

### Thu, Jan 15

#### Topic(s)

- Structure of the course
- Levels of analysis
- Causality in brain and behavior
- Does neuroscience need behavior? What does psychology need?

#### Read/Watch

- Required
  - @Krakauer2017-xl
  - @Parada2018-rp
  - @Newcombe2017-wu
- Recomended
  - @Siddiqi2022-wl
  - @Churchland1988-aj
  - @Favela2020-uc
  - @Ross2024-nr
  - @National_Geographic2014-gv
  
#### Materials

- [Slides](slides/wk-01-2026-01-15-intro.qmd) 

#### Assignments

```{r}
#| echo: false

ex_lvl_due <- psy_511_vars |>
  dplyr::filter(name == "WK_02_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Assigned*: [Exercise LVL • Levels/Terms](exercises/ex-LVL.html)
  - *Due*: `{r} ex_lvl_due`
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981371) 

## Week 02: Jan 19-23

### Thu, Jan 22

#### Topics

- Neuroanatomy

#### Read/Watch

- Required
  - @Leicester-Medical-School-Radiology2021-ck (Through ~ 8:20)
  - [Neuroanatomy notes](resources/anatomy.qmd)
- Recommended
  - @Challenged2025-cc
  - @Challenged2025-ff

#### Materials

- [Slides](slides/wk-02-2026-01-22-anatomy.qmd) 
- [Allen Brain Atlas](http://atlas.brain-map.org/atlas?atlas=138322605#atlas=138322605&structure=10390&resolution=119.78&x=31680.307112068967&y=42751.00179211847&zoom=-6&plate=112360949).

#### Assignments

```{r}
#| echo: false
#| label: calc-ex_anat_due
ex_anat_due <- psy_511_vars |>
  dplyr::filter(name == "WK_03_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise LVL • Levels/Terms](exercises/ex-LVL.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981371)
- *Assigned*: [Exercise ANAT • Neuroanatomy](exercises/ex-ANAT.qmd) 
  - *Due*: `{r} ex_anat_due`
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981392)

## Week 03: Jan 26-30

### Thu, Jan 29

#### Topic(s)

- Action

#### Read/Watch

- Required
  - @Shenoy2013-zi
  - @Goulding2025-pu
- Recommended
  - @Unknown2023-rt
  - @TED2011-oz
  - @Niu-Jin-Ji-Chu-Sheng-Wu-Xue-2021-mv

<!-- #### Materials -->

<!-- - [Action notes](404.qmd) -->

#### Assignments

- *Due*: [Exercise ANAT • Neuroanatomy](exercises/ex-ANAT.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981392)

## Week 04: Feb 2-6

### Thu, Feb 05

#### Topic(s)

- Perception

#### Read/Watch

- Required
  - @Rosenberg2023-km
  - @Khalsa2018-gf
- Recommended
  - @Neuroscience2025-ou
  - @CrashCourse2015-fn

<!-- #### Materials -->

<!-- - [Perception notes](404.qmd) -->

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_pa_due
ex_pa_due <- psy_511_vars |>
  dplyr::filter(name == "WK_05_DATE") |>
  dplyr::select(value) |>
  as.character()
```

```{r}
#| echo: false
#| label: calc-final_proj_prop_due
final_proj_prop_due <- psy_511_vars |>
  dplyr::filter(name == "WK_08_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Assigned*: [Final project proposal](exercises/final-project.qmd)
  - *Due*: `{r} final_proj_prop_due`
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005251)
- *Assigned*: [Exercise PA • Perception & Action](exercises/ex-PA.qmd)
  - *Due*: `{r} ex_pa_due`. 
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005038) 

## Week 05: Feb 9-13

### Thu, Feb 12

#### Topic(s)

- Learning & memory

#### Read/Watch

- Required
  - @Squire2011-zg
  - @DEsposito2015-zm

#### Assignment(s)

- *Due*: [Exercise PA • Perception & Action](exercises/ex-PA.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005038)

## Week 06: Feb 16-20

### Thu, Feb 19

#### Topic(s)

- Language

#### Read/Watch

- Required
  - @Hickok2007-rc
  - @Bourguignon2025-sy
  - @Hagoort2014-au

<!-- #### Materials -->

<!-- #### Assignment(s) -->

## Week 07: Feb 23-27 

### Thu, Feb 26

#### Topic(s)

- Emotion

#### Read/Watch

- Required
  - @Malezieux2023-as
  - @Watabe-Uchida2017-gi
  - @Siegel2018-ab
- Recommended
  - @LeDoux2000-qi

<!-- #### Materials -->

<!-- - [Notes](resources/fear-stress-reward.qmd) -->

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_emo_due
ex_emo_due <- psy_511_vars |>
  dplyr::filter(name == "WK_08_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Assigned*: [Exercise EMO • Measuring emotion](exercises/ex-EMO.qmd)
  - *Due*: `{r} ex_emo_due`
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005124)

## Week 08: Mar 2-6 

### Thu, Mar 5

#### Topic(s)

- Sleep & circadian rhythms

#### Read/Watch

- Required
  - @Nir2010-xd
  - @Rasch2013-yn

<!-- #### Materials -->

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_zz_due
ex_zz_due <- psy_511_vars |>
  dplyr::filter(name == "WK_09_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise EMO • Measuring emotion](exercises/ex-EMO.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005124)
- *Due*: [Final project proposal](exercises/final-project.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005251)
- *Assigned*: [Exercise ZZ • Sleep & Circadian Rhythms](exercises/ex-ZZ.qmd)
  - *Due*: `{r} ex_zz_due`
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005158)
  
## Spring Break: Mar 9-13 

**NO CLASS**

## Week 09: Mar 16-20

### Thu, Mar 19

#### Topic(s)

- Evolution & development of the nervous system

#### Read/Watch

- Required
  - @Sachkova2025-ma
  - @Stiles2010-cm
- Optional 
  - @Castrillon2023-mt
  - @Larsen2023-wx
  - @Rakic2009-jk
  - @Cao2017-bl
  - @Charvet2012-bg
  - @hofman_evolution_2014
  - @Blumberg2023-fs
  
<!-- #### Materials -->

<!-- - [Notes](resources/evolution.qmd) -->

#### Assignments

```{r}
#| echo: false
#| label: calc-ex_evo_due
ex_evo_due <- psy_511_vars |>
  dplyr::filter(name == "WK_10_DATE") |>
  dplyr::select(value) |>
  as.character()
```

```{r}
#| echo: false
#| label: calc-ex_dev_due
ex_dev_due <- psy_511_vars |>
  dplyr::filter(name == "WK_11_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise ZZ • Sleep & Circadian Rhythms](exercises/ex-ZZ.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005338)
- *Assigned*: [Exercise EVO • Evolution](exercises/ex-EVO.qmd)
  - *Due*: `{r} ex_evo_due`.
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005262)
- *Assigned*: [Exercise DEV • Development](exercises/ex-DEV.qmd)
  - *Due*: `{r} ex_dev_due`.
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005338)
  
## Week 10: Mar 23-27

### Thu, Mar 26

#### Topic(s)

- Cellular neuroscience I
  - Anatomy
  - Physiology
    - Resting potential

#### Read/Watch

- [Cellular neuroscience notes](404.qmd) | [PDF](404.qmd) |
- Optional
  - @Won2025-aq
  - @Zeng2017-sg
  - @Oliveira2015-ky
  - @Distefano-Gagne2023-gt

<!-- #### Materials -->

<!-- - [Slides](404.qmd) | [PDF](404.qmd) | -->

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_phys_due
ex_phys_due <- psy_511_vars |>
  dplyr::filter(name == "WK_11_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Assigned*: [Exercise PHYS • Neurophysiology I](exercises/ex-PHYS.qmd)
  - *Due*: `{r} ex_phys_due`
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005427)

## Week 11: Mar 30 - Apr 3

### Thu, Apr 02

#### Topics

- Cellular neuroscience II
  - Action potential
  - Synaptic transmission

#### Read/Watch

- [Cellular neuroscience notes](404.qmd)

<!-- #### Materials -->

<!-- - [Slides]() -->

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_ap_due
ex_ap_due <- psy_511_vars |>
  dplyr::filter(name == "WK_12_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise DEV • Development](exercises/ex-DEV.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005338)
- *Due*: [Exercise PHYS • Neurophysiology I](exercises/ex-PHYS.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005427)
- *Assigned*: [Exercise AP • Neurophysiology II](exercises/ex-AP.qmd)
  - *Due*: `{r} ex_ap_due`
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005465)

## Week 12: Apr 6-10

### Thu, Apr 09

#### Topic(s)

- Neurochemistry
  - Neurotransmitters
  - Hormones
- Neurocomputing

#### Read/Watch

- [Neurochemistry notes](404.qmd)
- Optional: @Sarkar2016-qf.

<!-- #### Materials -->

<!-- - [Slides]() -->

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_chem_due
ex_chem_due <- psy_511_vars |>
  dplyr::filter(name == "WK_13_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*:  [Exercise AP • Neurophysiology II](exercises/ex-AP.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005465)
- *Assigned*: [Exercise CHEM • Neurochemistry](exercises/ex-CHEM.qmd)
  - *Due*: `{r} ex_chem_due`.
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005510)

## Week 13: Apr 13-17

### Thu, Apr 16

#### Topic(s)

- Disorder & disease I

#### Read/Watch

- Required
  - @Howes2023-vk
  - @Volk2015-ki

<!-- #### Materials -->

<!-- - [Notes](resources/schizophrenia.qmd) -->

#### Assignment(s)

- *Due*: [Exercise CHEM • Neurochemistry](exercises/ex-CHEM.qmd)
  - [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005510)

## Week 14: Apr 20-24

### Thu, Apr 23

#### Topic(s)

- Disorder & disease II

#### Read/Watch

- Required
  - @Moncrieff2022-os
  - @Namkung2017-gc

<!-- #### Materials -->

<!-- - [Notes](resources/affective-disorders.qmd) -->

## Week 15: Apr 27 - May 1 

### Thu, Apr 30

#### Topics

- Frontiers in the biology of behavior
- Beethoven and the Cerebral Symphony

<!-- #### Materials -->

<!-- - [Slides]() -->

## Finals: May 4-8

### Thu, May 07

- [Final Project](exercises/final-project.qmd) write-up due
  - [Canvas dropbox](https://psu.instructure.com/courses/2379931/assignments/17170786)
