```{r}
#| echo: false

psy_511_vars <- readr::read_csv("data/csv/psy-511-vars.csv", show_col_types = FALSE)
```

## Week 01: Jan 12-16

### Thu, Jan 15

#### Topic(s)

- Structure of the course
- Levels of analysis
- Causality in brain and behavior
- Does neuroscience need behavior? What does psychology need?

#### Readings

- Required:
  - @Krakauer2017-xl
  - @Parada2018-rp
  - @Newcombe2017-wu
- Optional:
  - @Siddiqi2022-wl
  - @Churchland1988-aj
  - @Favela2020-uc
  - @Ross2024-nr
  
#### Materials

- [Slides](404.qmd)

#### Assignments

```{r}
#| echo: false

ex_lvl_due <- psy_511_vars |>
  dplyr::filter(name == "WK_02_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Assigned*: [Exercise LVL • Levels/Terms](exercises/ex-LVL.html). *Due*: `{r} ex_lvl_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981371) |

## Week 02: Jan 19-23

### Thu, Jan 22

#### Topics

- Neuroanatomy

#### Readings

- [Neuroanatomy notes](resources/anatomy.qmd)

#### Materials

- [Slides](). [PDF]()
- [Allen Brain Atlas](http://atlas.brain-map.org/atlas?atlas=138322605#atlas=138322605&structure=10390&resolution=119.78&x=31680.307112068967&y=42751.00179211847&zoom=-6&plate=112360949).

#### Assignments

```{r}
#| echo: false
#| label: calc-ex_anat_due
ex_anat_due <- psy_511_vars |>
  dplyr::filter(name == "WK_03_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise LVL • Levels/Terms](exercises/ex-LVL.qmd). [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981371)
- *Assigned*: [Exercise ANAT • Neuroanatomy](exercises/ex-ANAT.qmd). *Due*: `{r} ex_anat_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981392) |

## Week 03: Jan 26-30

### Thu, Jan 29

#### Topic(s)

- Action

#### Reading(s)

- @Shenoy2013-zi

#### Materials

- [Action notes](resources/action.qmd)

#### Assignments

- *Due*: [Exercise ANAT • Neuroanatomy](exercises/ex-ANAT.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/17981392) |

## Week 04: Feb 2-6

### Thu, Feb 05

#### Topic(s)

- Perception

#### Readings

- @Khalsa2018-gf
- @Shenoy2013-zi

#### Materials

- [Perception notes](resources/perception.qmd)

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_pa_due
ex_pa_due <- psy_511_vars |>
  dplyr::filter(name == "WK_05_DATE") |>
  dplyr::select(value) |>
  as.character()
```

```{r}
#| echo: false
#| label: calc-final_proj_prop_due
final_proj_prop_due <- psy_511_vars |>
  dplyr::filter(name == "WK_08_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Assigned*: [Final project proposal](exercises/final-project.qmd). *Due*: `{r} final_proj_prop_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005251) |
- *Assigned*: [Exercise PA • Perception & Action](exercises/ex-PA.qmd). *Due*: `{r} ex_pa_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005038) |

## Week 05: Feb 9-13

### Thu, Feb 12

#### Topic(s)

- Learning & memory

#### Readings

#### Materials

#### Assignment(s)

- *Due*: [Exercise PA • Perception & Action](exercises/ex-PA.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005038) |

## Week 06: Feb 16-20

### Thu, Feb 19

#### Topic(s)

- Emotion

#### Readings

- @Malezieux2023-as
- @Watabe-Uchida2017-gi

#### Materials

- [Notes](resources/fear-stress-reward.qmd)

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_emo_due
ex_emo_due <- psy_511_vars |>
  dplyr::filter(name == "WK_07_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Assigned*: [Exercise EMO • Measuring emotion](exercises/ex-EMO.qmd). *Due*: `{r} ex_emo_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005124) |

## Week 07: Feb 23-27 

### Thu, Feb 26

#### Topic(s)

- Sleep & circadian rhythms

#### Readings

#### Materials

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_zz_due
ex_zz_due <- psy_511_vars |>
  dplyr::filter(name == "WK_08_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise EMO • Measuring emotion](exercises/ex-EMO.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005124) |
- *Assigned*: [Exercise ZZ • Sleep & Circadian Rhythms](exercises/ex-ZZ.qmd). *Due*: `{r} ex_zz_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005158) |

#### Readings

#### Materials

## Week 08: Mar 2-6 

### Thu, Mar 5

#### Topic(s)

- Evolution of the nervous system

#### Readings

- Required:
  - @Charvet2012-bg
  - @hofman_evolution_2014
- Optional: 
  - @Castrillon2023-mt

#### Materials

- [Notes](resources/evolution.qmd)

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_evo_due
ex_evo_due <- psy_511_vars |>
  dplyr::filter(name == "WK_09_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Final project proposal](exercises/final-project.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005251) |
- *Due*: [Exercise ZZ • Sleep & Circadian Rhythms](exercises/ex-ZZ.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005338) |
- *Assigned*: [Exercise EVO • Evolution](exercises/ex-EVO.qmd). *Due*: `{r} ex_evo_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005262) |

## Spring Break: Mar 9-13 

**NO CLASS**

## Week 09: Mar 16-20

### Thu, Mar 19

#### Topic(s)

- Development of the nervous system

#### Readings

- Required:
  - @Cao2017-bl
  - @Blumberg2023-fs
- Optional:
  - @Larsen2023-wx
  - @Rakic2009-jk

#### Materials

- [Notes](resources/development.qmd)

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_dev_due
ex_dev_due <- psy_511_vars |>
  dplyr::filter(name == "WK_10_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise EVO • Evolution](exercises/ex-EVO.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005262) | 
- *Assigned*: [Exercise DEV • Development](exercises/ex-DEV.qmd). *Due*: `{r} ex_dev_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005338) |

## Week 10: Mar 23-27

### Thu, Mar 26

#### Topics

- Cellular neuroscience I
  - Anatomy
  - Physiology
    - Resting potential

#### Readings

- [Cellular neuroscience notes](resources/cells.html) | [PDF](resources/cells.pdf) |
- Optional:
  - @Zeng2017-sg
  - @Oliveira2015-ky
  - @Distefano-Gagne2023-gt

#### Materials

- [Slides](404.qmd) | [PDF](404.qmd) |

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_phys_due
ex_phys_due <- psy_511_vars |>
  dplyr::filter(name == "WK_11_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise DEV • Development](exercises/ex-DEV.qmd) | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005338) |
- *Assigned*: [Exercise PHYS • Neurophysiology I](exercises/ex-PHYS.qmd). *Due*: `{r} ex_phys_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005427) |

## Week 11: Mar 30 - Apr 3

### Thu, Apr 02

#### Topics

- Cellular neuroscience II
  - Action potential
  - Synaptic transmission

#### Readings

- [Cellular neuroscience notes](resources/cells.qmd)

#### Materials

- [Slides]()

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_ap_due
ex_ap_due <- psy_511_vars |>
  dplyr::filter(name == "WK_12_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*: [Exercise PHYS • Neurophysiology I](exercises/ex-PHYS.qmd) | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005427) |
- *Assigned*: [Exercise AP • Neurophysiology II](exercises/ex-AP.qmd). *Due*: `{r} ex_ap_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005465) |

## Week 12: Apr 6-10

### Thu, Apr 09

#### Topics

- Neurochemistry
  - Neurotransmitters
  - Hormones
- Neurocomputing

#### Readings

- [Neurochemistry notes](resources/neurochemistry.qmd)
- Optional: @Sarkar2016-qf.

#### Materials

- [Slides]()

#### Assignment(s)

```{r}
#| echo: false
#| label: calc-ex_chem_due
ex_chem_due <- psy_511_vars |>
  dplyr::filter(name == "WK_13_DATE") |>
  dplyr::select(value) |>
  as.character()
```

- *Due*:  [Exercise AP • Neurophysiology II](exercises/ex-AP.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005465) |
- *Assigned*: [Exercise CHEM • Neurochemistry](exercises/ex-CHEM.qmd). *Due*: `{r} ex_chem_due`. | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005510) |

## Week 13: Apr 13-17

### Thu, Apr 16

#### Topics

- Disorder & disease I

#### Readings

- @Howes2023-vk
- @Volk2015-ki

#### Materials

- [Notes](resources/schizophrenia.qmd)

#### Assignment(s)

- *Due*: [Exercise CHEM • Neurochemistry](exercises/ex-CHEM.qmd). | [Canvas dropbox](https://psu.instructure.com/courses/2441266/assignments/18005510) |

## Week 14: Apr 20-24

### Thu, Apr 23

#### Topics

- Disorder & disease II

#### Readings

- @Moncrieff2022-os
- @Namkung2017-gc

#### Materials

- [Notes](resources/affective-disorders.qmd)

## Week 15: Apr 27 - May 1 

### Thu, Apr 30

#### Topics

- Frontiers in the biology of behavior
- Beethoven and the Cerebral Symphony

#### Materials

- [Slides]()

## Finals: May 4-8

### Thu, May 07

- [Final Project](exercises/final-project.qmd) write-up due. | [Canvas dropbox](https://psu.instructure.com/courses/2379931/assignments/17170786) |
